### 2012-08-21 doc/prelim/document/frontmatter/abstract.tex
frontmatter updates

%        File: thesis_proposal.tex
%
\documentclass[letterpaper,12pt]{article}
\usepackage[top=1.0in,bottom=1.0in,left=1.25in,right=1.25in]{geometry}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage[usenames]{color}
\usepackage[
naturalnames = true, 
colorlinks = true, 
linkcolor = black,
anchorcolor = black,
citecolor = black,
menucolor = black,
urlcolor = blue
]{hyperref}

%%---------------------------------------------------------------------------%%
\author{Stuart R. Slattery
\\ \href{mailto:sslattery@wisc.edu}{\texttt{sslattery@wisc.edu}}
}

\date{\today}
\title{Thesis Proposal:\\
  A Massively Parallel Stochastic Method for Nonlinear Problems}
\begin{document}
\maketitle

%%---------------------------------------------------------------------------%%
\section{Introduction}
In many fields of engineering and physics, nonlinear problems are a
primary focus of study. Recent focus on multiple physics systems (and
in particular nuclear systems) adds a new level of complexity to
common nonlinear systems as solution strategies change when they are
coupled to other problems. Furthermore, a desire for predictive
simulations to enhance the safety and performance of engineered
systems creates a need for extremely high fidelity computations to be
performed for these coupled systems as a means to capture effects not
modeled by coarser methods. In order to achieve this high fidelity,
state-of-the-art computing facilities must be leveraged in a way that
is both efficient and considerate of hardware-related issues. As
scientific computing moves towards exascale facilities with machines
of $O(1,000,000)$ cores already coming online, new algorithms to solve
these complex problems must be developed to leverage this new
hardware. Issues such as resiliency to node failure and scaling to
large numbers of cores will be pertinent to robust algorithms aimed at
this new hardware. Considering these issues, this thesis proposes a
novel stochastic method to advance solution techniques for nonlinear
problems with a focus on coupled physics systems.

@@

%%---------------------------------------------------------------------------%%
\section{Deliverables}

This work will deliver the following items:

\begin{itemize}
\item Develop a massively parallel strategy for the MCSA method for
  sparse linear systems.
\item Implement a massively parallel strategy for the MCSA method for
  sparse linear systems.
\item Fully assess the performance of parallel MCSA on leadership class
  computing systems in order to determine its feasibility using
  benchmark problems.
\item Compare the performance of MCSA to other iterative methods for
  sparse linear systems including GMRES.
\item Develop the FANM method for nonlinear systems.
\item Implement the FANM method for nonlinear systems.
\item Fully assess the performance of the FANM method on leadership
  class computing systems using model problems.
\item Compare the performance of MCSA to other nonlinear methods
  including JFNK.
\end{itemize}

This work will not address the resiliency of these algorithms.

%%---------------------------------------------------------------------------%%
\section{Dissertation Outline}

Based on the above work, the dissertation can be outlined in five
distinct parts:

\begin{enumerate}
\item Iterative methods for sparse linear systems (fixed-point,
  subspace, and stochastic methods).
\item MCSA and Multiple Set Overlapping Domain Decomposition
  (development and implementation).
\item Iterative methods for nonlinear systems (Newton methods).
\item FANM (developement and implementation).
\item Application to model problems (conduction, Navier-Stokes,
  conjugate heat transfer).
\end{enumerate}

%%---------------------------------------------------------------------------%%
\section{Committee}

\begin{itemize}
\item Paul Wilson (advisor): Associate Professor, Department of
  Engineering Physics.
\item Greg Moses: Professor, Department of Engineering Physics.
\item Carl Sovinec: Professor, Department of Engineering Physics.
\item Chris Rutland: Professor, Deptartment of Mechanical Engineering.
\item Tom Evans: Distinguished R\&D Staff, Reactor and Nuclear Systems
  Division, Oak Ridge National Laboratory.

\end{itemize}

%%---------------------------------------------------------------------------%%
\section{Timeline}

%%---------------------------------------------------------------------------%%
\pagebreak
\bibliographystyle{ieeetr}
\bibliography{references}
\end{document}

>>>>

\svnidlong{$LastChangedBy$}{$LastChangedRevision$}{$LastChangedDate$}{$HeadURL: http://freevariable.com/dissertation/branches/diss-template/frontmatter/abstract.tex $}
\vcinfo{}

In many fields of engineering and physics, nonlinear problems are a
primary focus of study. Recent focus on multiple physics systems (and
in particular nuclear systems) adds a new level of complexity to
common nonlinear systems as solution strategies change when they are
coupled to other problems. Furthermore, a desire for predictive
simulations to enhance the safety and performance of engineered
systems creates a need for extremely high fidelity computations to be
performed for these coupled systems as a means to capture effects not
modeled by coarser methods. In order to achieve this high fidelity,
state-of-the-art computing facilities must be leveraged in a way that
is both efficient and considerate of hardware-related issues. As
scientific computing moves towards exascale facilities with machines
of $O(1,000,000)$ cores already coming online, new algorithms to solve
these complex problems must be developed to leverage this new
hardware. Issues such as resiliency to node failure and scaling to
large numbers of cores will be pertinent to robust algorithms aimed at
this new hardware. Considering these issues, this thesis proposes a
novel stochastic method to advance solution techniques for nonlinear
problems with a focus on coupled physics systems.

@@
